Polytope notes

### 2020-03-22 notes/bo-FSD.tex
started FSD proof

\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage{mathtools, amsthm, amsmath, amssymb, graphicx, verbatim}
%\usepackage[thmmarks, thref, amsthm]{ntheorem}
\usepackage{color}
\usepackage{wrapfig}
\usepackage{subcaption}
\usepackage[colorinlistoftodos,textsize=tiny]{todonotes} % need xargs for below
%\usepackage{accents}
\usepackage{bbm}
\usepackage{xspace}

\usetikzlibrary{calc}
\newcommand{\Comments}{1}
\newcommand{\mynote}[2]{\ifnum\Comments=1\textcolor{#1}{#2}\fi}
\newcommand{\mytodo}[2]{\ifnum\Comments=1%
  \todo[linecolor=#1!80!black,backgroundcolor=#1,bordercolor=#1!80!black]{#2}\fi}
\newcommand{\raf}[1]{\mynote{green}{[RF: #1]}}
\newcommand{\raft}[1]{\mytodo{green!20!white}{RF: #1}}
\newcommand{\jessie}[1]{\mynote{purple}{[JF: #1]}}
\newcommand{\jessiet}[1]{\mytodo{purple!20!white}{JF: #1}}
\newcommand{\bo}[1]{\mynote{blue}{[Bo: #1]}}
\newcommand{\botodo}[1]{\mytodo{blue!20!white}{[Bo: #1]}}
\ifnum\Comments=1               % fix margins for todonotes
  \setlength{\marginparwidth}{1in}
\fi

\newcommand{\reals}{\mathbb{R}}
\newcommand{\posreals}{\reals_{>0}}%{\reals_{++}}
\newcommand{\dom}{\mathrm{dom}}

@@

\bo{Not sure how to integrate this notation into the rest of the document.}

Let some norm $\|\cdot\|$ on finite-dimensional Euclidean space be given.
Given a set $T$ and a point $u$, let $d(T,u) = \inf_{t \in T} \|t-u\|$.

Given two sets $T,T'$, let $d(T,T') = \inf_{t\in T, t' \in T'} \|t-t'\|$.

Let the ``thickening'' $B(T,\epsilon)$ be defined as
  \[ B(T,\epsilon) = \{u \in \R' : d(T,u) < \epsilon \} . \]

We are given an original loss $\ell$ with property $\gamma$ and finite report space $\R$; and a polyhedral embedding with loss $L$, property, $\Gamma$, report space $\R' \subseteq \reals^d$, and embedding points $\{u_r : r \in \R\}$.

Let $\mathcal{S} \subseteq 2^{\R}$ be defined as $\mathcal{S} = \{\gamma(p) : p \in \Delta_{\Y}\}$.
In other words, for each $p$, we take the set of optimal reports $R = \gamma(p) \subseteq \R$, and we add $R$ to $\mathcal{S}$.

Let $\mathcal{U} \subseteq 2^{\reals^d}$ be defined as $\mathcal{U} = \{\Gamma(p) : p \in \Delta_{\Y}\}$.

\begin{lemma} \label{lemma:U-convex-closed}
  $\mathcal{U}$ is a finite set, and each element $U$ is a closed, convex polyhedron.
\end{lemma}
\begin{proof}
  \raf{I updated the main doc to include a proof of exactly this statement.  It made me realize that the existing proof was wrong, and this is actually the right thing to show anyway!}
  \bo{More of a sketch right now}
  Let $p$ be in the interior of the simplex.
  For any such $p$, the polyhedral expected loss $L(\cdot;p)$ projects down to the same fixed power diagram over $\reals^d$.
  The minimizer of a polyhedral loss is always the projection of some face of the polyhedron, \bo{cite} so there are a finite number of possible minimizers and each is a closed, convex polyhedron (being a member of the power diagram or an intersection of members).
  Now for $p$ not in the interior, consider each of finitely many subsets of the outcome space and restrict $p$ to have support on this subset; repeat the above arguments.
  The total number of report sets $U$ is still finite, each a closed, convex polyhedron.
\end{proof}

\begin{lemma} \label{lemma:U-surject}
  There is a surjection from $\mathcal{U}$ to $\mathcal{S}$ where $U \mapsto R$ if, for some $p$, we have $\gamma(p) = U$ and $\Gamma(p) = R$.
  We write $R_U$ for the value of this map at $U$.
\end{lemma}
\begin{proof}
  For each report $r$, write $u_r$ for its embedding point and for each $U \in \mathcal{U}$, let $R_U = \{r : u_r \in U\}$.
  Recall that $\mathcal{U}$ is the collection of sets $U = \gamma(p)$ for some $p$, while $\mathcal{S}$ is the collection of sets $R = \Gamma(p)$ for some $p$.
  By definition of embedding, we have for any $p$ that $u_r \in \Gamma(p) \iff r \in \gamma(p)$.
  So if $U = \Gamma(p)$, we must have $R_U = \gamma(p)$.
  This shows that $R_U \in \mathcal{S}$ for all $U$, and furthermore, the map is surjective because every $R \in \mathcal{S}$ is equal to $R_U$ for some $U \in \mathcal{U}$.
\end{proof}

The next lemma shows that if a subset of $\mathcal{U}$ intersect, then their corresponding report sets intersect as well.
\begin{lemma} \label{lemma:calibrated-pos}
  Let $\mathcal{U}' \subseteq \mathcal{U}$.
  If $\cap_{U\in\mathcal{U}'} U \neq \emptyset$ then $\cap_{U\in\mathcal{U}'} R_U \neq \emptyset$.
\end{lemma}
\begin{proof}
  Let $u \in \cap_{U\in\mathcal{U}'} U$.
  Then there is some $r$ such that $\Gamma_u \subseteq \gamma_r$. \bo{This follows because $L$ embedding $\ell$ implies $L$ indirectly elicits $\ell$. Uses trim.}
  Therefore, if we have $p$ such that $u$, then $r$ is optimal.
  Since $u \in U$, we have $r \in R_U$.
  This holds for all $U \in \mathcal{U}'$, so $r \in \cap_{U\in\mathcal{U}'} R_U$, so it is nonempty.
\end{proof}

%% Bo: I thought this might be useful, but guess not.
%\begin{lemma}
%  Let $\{U_j : j \in \mathcal{J}\}$ be a finite collection of closed, convex sets.
%  If $u \not\in \cap_j U_j$, then for all small enough $\epsilon > 0$, $u \not\in \cap_j B(U_j,\epsilon)$.
%\end{lemma}
%\begin{proof}
%  Consider the collection $\{U_j : j \in \mathcal{J}\}$ and suppose $u \not \in \cap_j U_j$.
%  In particular, there exists some $U$ in the collection such that $u \not\in U$.
%  Because $U$ is closed and convex, that there exists $\epsilon' > 0$ such that $d(U,u) \geq \epsilon'$.
%  So for all $\epsilon < \epsilon'$, we have $u \not\in B(U,\epsilon)$.
%  This implies $u \not\in \cap_j B(U_j,\epsilon)$.
%\end{proof}
%

\begin{lemma} \label{lemma:enclose-halfspaces}
  Let $D$ be a closed, convex polyhedron in $\reals^d$.
  For any $\epsilon > 0$, there exists an open, convex polyhedron $D'$, the intersection of a finite number of open halfspaces, such that
    \[ D \subseteq D' \subseteq B(D,\epsilon) . \]
\end{lemma}
\begin{proof}
  Let $S$ be the standard open $\epsilon$-ball $B(\{\vec{0}\},\epsilon)$.
  Note that $B(D,\epsilon) = D + S$ where $+$ is the Minkowski sum.
%  Now let $S' = \{u : \|u\|_1 < \delta\}$ be the open $\delta$ ball in $L_1$ norm.
%  By equivalence of norms in Euclidean space, \bo{cite} we can take $\delta$ small enough yet positive such that $S' \subseteq S$.
%  By Lemma \ref{lemma:open-plus-closed-poly}, the Minkowski sum $D' = D + S'$ is an open polyhedron, i.e. the intersection of a finite number of open halfspaces.
  Now let $S' = \{u : \|u\|_1 \leq \delta\}$ be the closed $\delta$ ball in $L_1$ norm.
  By equivalence of norms in Euclidean space, \bo{cite} we can take $\delta$ small enough yet positive such that $S' \subseteq S$.
  By standard results, the Minkowski sum of two closed, convex polyhedra, $D'' = D + S'$ is a closed polyhedron, i.e. the intersection of a finite number of closed halfspaces. (A proof: we can form the higher-dimensional polyhedron $\{(x,y,z) : x \in D, y \in S', z = x+y\}$, then project onto the $z$ coordinates.)

  Now, if $T' \subseteq T$, then the Minkowksi sum satisfies $D + T' \subseteq D + T$.
  In particular, because $\emptyset \subseteq S' \subseteq S$, we have
    \[ D \subseteq D'' \subseteq B(D,\epsilon) . \]
  Now let $D'$ be the interior of $D''$, i.e. if $D'' = \{x : Ax \leq b\}$, then we let $D' = \{x: Ax < b\}$.
  We retain $D' \subseteq B(D,\epsilon)$.
  Further, we retain $D \subseteq D'$, because $D$ is contained in the interior of $D'' = D + S'$.
  (Proof: if $x \in D$, then for some $\gamma$, $x + B(\{\vec{0}\},\gamma) = B(x,\gamma)$ is contained in $D + S'$.)
  This proves the lemma.
\end{proof}

\begin{lemma} \label{lemma:thick-nonempty}
  Let $\{U_j : j \in \mathcal{J}\}$ be a finite collection of closed, convex sets with $\cap_{j\in\mathcal{J}} U_j \neq \emptyset$.
  Then there exists  $\epsilon > 0$ such that $\cap_j B(U_j,\epsilon) \subseteq B(\cap_j U_j, \delta)$.
  \raft{FYI, formalized some of the English in both the statement and proof}
\end{lemma}
\begin{proof}
  We induct on $|\mathcal{J}|$.
  If $|\mathcal{J}|=1$, set $\epsilon = \delta$.
  If $|\mathcal{J}|>1$, let $j\in\mathcal{J}$ be arbitrary, let $U' = \cap_{j'\neq j} U_{j'}$, and let $C(\epsilon) = \cap_{j' \neq j} B(U_{j'},\epsilon)$.
  Let $D = U_j \cap U'$.
  We must show that $B(U_j,\epsilon) \cap C(\epsilon) \subseteq B(D,\delta)$.
  By Lemma \ref{lemma:enclose-halfspaces}, we can enclose $D$ strictly within a polyhedron $D'$, the intersection of a finite number of open halfspaces, which is itself strictly enclosed in $B(D,\delta)$.
  (For example, if $D$ is a point, then enclose it in a hypercube, which is enclosed in the ball $B(D,\delta)$.)
%  \raf{We can use the fact that the $U_j$ are all polyhedral here, so $D$ is polyhedral as well.  Now let $B_1()$ be a ball with respect to $\|\cdot\|_1$, and observe that $B_1(D,\delta')$ is therefore also polyhedral for all $\delta'$.  Using norm bounds, we can find a small enough $\delta'$ so that $B_1(D,\delta') \subseteq B(D,\delta)$.}
  We will prove that, for small enough $\epsilon$, $B(U_j,\epsilon) \cap C(\epsilon)$ is contained in $D'$.
  This implies that it is contained in $B(D,\delta)$.

  For each halfspace defining $D'$, consider its complement $F$, a closed halfspace.
  We prove that $F \cap B(U_j,\epsilon) \cap C(\epsilon) = \emptyset$.
  Consider the intersections of $F$ with $U$ and $U'$, call them $G$ and $G'$.
  These are closed, convex sets that do not intersect (because $D$ in contained in the complement of $F$).
  So $G$ and $G'$ are separated by a nonzero distance, so $B(G,\gamma) \cap B(G',\gamma) = \emptyset$ for small enough $\gamma$.
  And $B(G,\gamma) = F \cap B(U_j,\gamma)$ while $B(G',\gamma) = F \cap B(U',\gamma)$.
  This proves that $F \cap B(U_j,\gamma) \cap B(U',\gamma) = \emptyset$.
  By inductive assumption, $C(\epsilon) \subseteq B(U',\gamma)$ for small enough $\epsilon = \epsilon_F$.
  So $F \cap B(U_j,\gamma) \cap C(\epsilon) = \emptyset$.
  We now let $\epsilon$ be the minimum over these finitely many $\epsilon_F$ (one per halfspace).
\end{proof}

\begin{figure}
\caption{Illustration of a special case of the proof of Lemma \ref{lemma:thick-nonempty} where there are two sets $U_1,U_2$ and their intersection $D$ is a point. We build the polyhedron $D'$ inside $B(D,\delta)$. By considering each halfspace that defines $D'$, we then show that for small enough $\epsilon$, $B(U_1,\epsilon)$ and $B(U_2,\epsilon)$ do not intersect outside $D'$. So the intersection is contained in $D'$, so it is contained in $B(D,\delta)$.}
\includegraphics[width=0.24\textwidth]{figs/separated-proof-2} \hfill
\includegraphics[width=0.24\textwidth]{figs/separated-proof-3} \hfill
\includegraphics[width=0.24\textwidth]{figs/separated-proof-4} \hfill
\includegraphics[width=0.24\textwidth]{figs/separated-proof-5}
\end{figure}

\begin{lemma} \label{lemma:thick-empty}
  Let $\{U_j : j \in \mathcal{J}\}$ be a finite collection of nonempty closed, convex sets with $\cap_{j\in\mathcal{J}} U_j = \emptyset$.
  Then for all $\delta > 0$, there exists  $\epsilon > 0$ such that $\cap_{j\in\mathcal{J}} B(U_j,\epsilon) = \emptyset$.
\end{lemma}
\begin{proof}
  By induction on the size of the family.
  Note that the family must have size at least two.
  Let $U_j$ be any set in the family and let $U' = \cap_{j' \neq j} U_{j'}$.
  There are two possibilities.

  The first possibility, which includes the base case where the size of the family is two, is the case $U'$ is nonempty.
  Because $U_j$ and $U'$ are non-intersecting closed convex sets, they are separated by some distance $\epsilon$.
  By Lemma \ref{lemma:thick-nonempty}, for any $\epsilon > 0$, there exists $\delta > 0$ such that $\cap_{j'\neq j} B(U_{j'},\delta) \subseteq B(U', \epsilon/3)$.
  Then we have $B(U_j, \epsilon/3) \cap B(U', \epsilon/3) = \emptyset$.

  The second possibility is that $U'$ is empty.
  This implies we are not in the base case, as the family must have three or more sets.
  By inductive assumption, for small enough $\delta$ we have $\cap_{j' \neq j} B(U_{j'},\delta) = \emptyset$, which proves this case.
\end{proof}

%\begin{lemma} \label{lemma:thick-int}
%  Let $\{U_j : j \in \mathcal{J}\}$ be a finite collection of closed, convex sets.
%  For any $\delta > 0$, there exists an $\epsilon > 0$ such that
%  \[ \cap_j B(U_j,\epsilon) \subseteq B\left(\cap_j U_j, \delta\right)  \]
%  where if $\cap_j U_j = \emptyset$, we interpret the right-hand side as $\emptyset$.
%\end{lemma}
%\begin{proof}
%  \raf{Maybe cleaner to break into to two parts right off the bat: $\cap U_j$ is empty or not?}
%  By induction on the size of the collection.
%  If the size is $1$, set $\epsilon = \delta$.
%  If the size is larger than $1$, let $U_j$ be any member of the collection, let $U' = \cap_{j'\neq j} U_{j'}$, and let $C(\epsilon) = \cap_{j' \neq j} B(U_{j'},\epsilon)$.
%  There are two cases.
%  If $U_j \cap U' = \emptyset$, then we must show that $B(U_j,\epsilon) \cap C(\epsilon) = \emptyset$.
%  Because $U_j,U'$ are both closed and convex, they are separated by some nonzero distance. So for some $\gamma > 0$, we have $B(U_j,\gamma) \cap B(U',\gamma) = \emptyset$.
%  By inductive assumption, for all small enough $\epsilon$, $C(\epsilon) \subseteq B(U',\gamma)$, so we have $B(U_j,\gamma) \cap C(\epsilon) = \emptyset$.
%  Choosing a small enough $\epsilon$ that is also less than $\gamma$ completes this case.
%
%  The other case is that $U_j \cap U' = D$, some nonempty closed convex set.
%  Here we must show that $B(U_j,\epsilon) \cap C(\epsilon) \subseteq B(D, \delta)$.
%  Enclose $D$ in the intersection of a finite number of open halfspaces, which is enclosed in $B(D,\delta)$. \bo{I am claiming this is possible, but I didn't prove it yet...}
%  We will prove that, for small enough $\epsilon$, $B(U_j,\epsilon) \cap C(\epsilon)$ is contained in this same intersection.
%  This implies that it is contained in $B(D,\delta)$.
%
%  For each halfspace, consider its complement $F$, a closed halfspace.
%  We prove that $F \cap B(U_j,\epsilon) \cap C(\epsilon) = \emptyset$.
%  Consider the intersections of $F$ with $U$ and $U'$, call them $G$ and $G'$.
%  These are closed, convex sets that do not intersect (because $D$ in contained in the complement of $F$).
%  So $G$ and $G'$ are separated by a nonzero distance, so $B(G,\gamma) \cap B(G',\gamma) = \emptyset$ for small enough $\gamma$.
%  And $B(G,\gamma) = F \cap B(U_j,\gamma)$ while $B(G',\gamma) = F \cap B(U',\gamma)$.
%  By inductive assumption, $C(\epsilon) \subseteq B(U',\gamma)$ for small enough $\epsilon$.
%  So $F \cap B(U_j,\epsilon) \cap C(\epsilon) = \left(F \cap B(U_j,\epsilon)\right) \cap \left(F \cap C(\epsilon)\right) = \emptyset$ for a small enough $\epsilon$.
%
%  We now take the minimum over these finitely many $\epsilon$'s (one per halfspace).
%\end{proof}

\begin{corollary} \label{cor:thick-intersect}
  There exists a small enough $\epsilon > 0$ such that, for any subset $\{U_j : j \in \mathcal{J}\}$ of $\mathcal{U}$, if $\cap_j U_j = \emptyset$, then $\cap_j B(U_j,\epsilon) = \emptyset$.
\end{corollary}
\jessiet{Mention $\mathcal{U}$ is finite for good measure?}
\raft{I think the proof makes it clear enough}
\begin{proof}
  For each subset, Lemma \ref{lemma:thick-empty} gives an $\epsilon$.
  We take the minimum over these finitely many choices.
\end{proof}

\begin{definition} \label{def:thick-link}
  Given polyhedral $L$ embedding some $\ell$, the \emph{$\epsilon$-thickened link} $\psi: \R' \to \R \cup \{\bot\}$ is constructed as follows.
  We will label each point $u \in \R'$ with a set of legal mappings $r \in \R$.
  Let $\Psi: \R' \toto \R$ be this labeling.
  Begin by initializing $\Psi(u) = \R$ for all $u$, i.e. all mappings are legal.
  Then, we apply the following iterative procedure.
  For each set $U \in \mathcal{U}$, for each $u \in B(U,\epsilon)$, we set $\Psi(u) = \Psi(u) \cap R_U$ where $R_U$ is given by Lemma \ref{lemma:U-surject}.
  Then, construct $\psi$ by making arbitrary legal choices, e.g. $\psi(u)$ is defined as the first element of $\R$ in $\Psi(u)$.
  If there is no legal choice because $\Psi(u) = \emptyset$, set $\psi(u) = \bot$.
\end{definition}

\begin{theorem} \label{thm:small-eps-thick}
  For all small enough $\epsilon$, the epsilon-thickened link $\psi$ is a well-defined link function from $\R'$ to $\R$, i.e. $\psi(u) \neq \bot$ for all $u$.
\end{theorem}
\begin{proof}
  Fix a small enough $\epsilon$ as promised by Corollary \ref{cor:thick-intersect}.
  Consider any $u \in \R'$.
  If $u$ is not in $B(U,\epsilon)$ for any $U \in \mathcal{U}$, then we have $\Psi(u) = \R$, so it is nonempty.
  Otherwise, let $\{U_j : j \in \mathcal{J}\}$ be the family whose thickenings intersect at $u$.
  By Corollary \ref{cor:thick-intersect}, because of our choice of $\epsilon$, the family themselves has nonempty intersection.
  By Lemma \ref{lemma:calibrated-pos}, their corresponding report sets $\{R_j : j \in \mathcal{J}\}$ also intersect at some $r$, so $\Psi(u)$ is nonempty.
\end{proof}

\begin{lemma} \label{lemma:distance-loss}
  If $L$ is a polyhedral loss, then for each $p$, there exists a constant $c$ such that, for all $u$,
    \[ L(u;p) - \inf_{u^* \in \R'} L(u^*;p) \geq c \cdot d(\Gamma(p),u) . \]
\end{lemma}
\begin{proof}
  Fix $p$ and let $U = \Gamma(p)$.
  If $u \in U$, then both sides are zero.
  So it remains to find a $c$ such that the inequality holds for all $u \not\in U$.

  \bo{Change $\underbar{L}$ to something like $\hat{L}$.}

  $L(\cdot;p)$ is a convex polyhedral function, so it is the pointwise maximum over finitely many linear functions.
  Construct the convex polyhedral function $\underbar{L}(\cdot;p)$ by dropping from the max those linear functions that are never equal to $L$ for any $u^* \in U$.
  We have $\underbar{L}(u^*;p) = L(u^*;p)$ for all $u^* \in U$ and $\underbar{L}(u;p) \leq L(u;p)$ for all $u \not\in U$.
  Now $\underbar{L}$ is the max over a finite number of linear functions.
  Each such function $f$ with gradient $\nabla f$ is equal to $\underbar{L}$ above a closed, convex cell in the power diagram formed by projecting $\underbar{L}(\cdot;p)$.
  If $f$ has nonzero gradient, its cell overlaps with $U$ exactly at some face of $U$.
  We will prove that there exists $c_f > 0$ such that, for all $u$ in the corresponding cell of the power diagram,
    \[ \underbar{L}(u;p) \geq L(u^*;p) + c_f \cdot d(U,u) . \]
  We will then repeat this for the finitely many $f$ with nonzero gradient (which covers all points $u \not\in U$) and take the minimum to obtain the desired $c > 0$.

  Consider the set of unit vectors $\{v \in \reals^d : \|v\|=1\}$ and the set of $u^*$ on the boundary of $U$.
  For all pairs $u^*,v$ such that $v$ exposes $u^*$, let
    \[ G_{u^*,v} = \left\{ u^* + \beta v : \beta \geq 0 \right\} . \]
  Note that $\{ u : u \not\in U\} \subseteq \cup_{u^*,v} G_{u^*,v}$.
  We claim each $G_{u^*,v}$ can be associated with some linear $f$ such that $f(u) = \underbar{L}(u;p)$ for all $u \in G_{u^*,v}$.
  \bo{Need to prove this; I think it follows because $G_{u^*,v}$ lies completely within some cell of the power diagram formed by projecting $\underbar{L}$.}
  Hence for all $u$ in $G_{u^*,v}$, we have
  \begin{align*}
    \underbar{L}(u;p) &= \underbar{L}(u^*;p) + (\nabla f) \cdot (d(u^*,u) v)  \\
                      &= L(u^*;p) + c_{u^*,v} \cdot d(U,u)
  \end{align*}
  where $c_{u^*,v} := (\nabla f) \cdot v$, and we note $u^* = \min_{u' \in U} d(u',u)$. \bo{Should prove this; ought to follow because $v$ exposes $u^*$.}
  We must have $c_{u^*,v} > 0$, otherwise $G_{u^*,v} \subseteq U$ which is a contradiction.

  Now for each $f$, we claim the set $\{u^*, v : \text{$G_{u^*,v}$ is associated with $f$}\}$ is closed.
  This follows because the set of $u^*$ such that $f(u^*) = \underbar{L}(u^*;p)$ is closed, and for fixed $u^*$, the set of $v$ such that $G_{u^*,v}$ is in the cell of the power diagram is also closed.\bo{Should prove this.}
  So for this $f$, the infimum over all positive $c_{u^*,v}$ is achieved by some positive member $c_f > 0$.
\end{proof}

\begin{theorem}
  For small enough $\epsilon$, the $\epsilon$-thickened link $\psi$ satisfies that, for all $p$, there exists $\delta > 0$ such that, for all $u \in \R'$,
    \[ L(u;p) - \inf_{u^* \in \R'} L(u^*;p) \geq \delta \left[ \ell(\psi(u);p) - \min_{r^* \in \R} \ell(r^*;p) \right] . \]
\end{theorem}
\begin{proof}
  We take the $\epsilon$ thickened link, which is well-defined by Theorem \ref{thm:small-eps-thick}.
  Fix $p$ and let $U = \Gamma(p)$.
  The left-hand side is nonnegative, so it suffices to prove the result for all $u$ such that the right side is strictly positive, i.e. for all $u$ such that $\psi(u) \not\in \gamma(p)$.
  By definition of the $\epsilon$-thickened link, we must have $d(U,u) \geq \epsilon$.
  By Lemma \ref{lemma:distance-loss}, we have $L(u;p) - \inf_{u^*} L(u^*;p) \geq C$ where $C = c\epsilon$ for some $c > 0$.
  This holds for all $u$.
  Meanwhile,
    \[ \ell(\psi(u);p) - \min_{r^*} \ell(r^*;p) \leq \max_{r \in \R} \ell(r;p) - \min_{r^* \in \R} \ell(r^*;p) =: D, \]
  for some constant $D$.
  This also holds for all $u$.
  Set $\delta = \frac{C}{D}$ to complete the proof.
\end{proof}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\break

Bo: this is the proof sketch of the stronger result that Raf and I discussed.

\begin{theorem}
  There exists $\delta$ such that, for all $p,u$,
    \[ L(u;p) - \inf_{u^*} L(u^*;p) \geq \delta \left[ \ell(\psi(u);p) - \min_{r^*} \ell(r^*;p) \right] . \]
\end{theorem}
\begin{proof}[Sketch]
  The above theorem gives a $\delta_p > 0$ for each $p$.
  \bo{Why doesn't this work? $\Delta_{\Y}$ is a closed set, so the infimum delta is positive, done.}

  \bo{The kind of argument we were using...}
  Fix $r^*$ and let $p^*$ be in the relative interior of the level set $\gamma_{r^*}$. (We have conditions implying that $\gamma_{r^*}$ is full-dimensional in the simplex...)
  Let $\{ p^b : b \in B\}$ be the relative boundary of the level set $\gamma_{r^*}$.
  It is indexed by, for example, the closed unit sphere $B = \{w : \|w\|=1\}$ via $p_b = \text{relbound}(\gamma_{r^*}) \cap \{p^* + \beta b : \beta \geq 0\}$.
  For $\alpha \in [0,1]$, define the distribution $p^b_{\alpha} := \alpha p^* + (1-\alpha) p^b$ 
  \begin{claim} \label{claim:p-bound-1}
    Fix $b$.
    There exists $\beta_b \in \reals$ such that $\inf_{u: d(U(p),u) \geq \epsilon} L(u;p^b_{\alpha}) - L(u^*;p^b_{\alpha}) \geq \alpha \beta_b$ for all $\alpha \in [0,1]$.
  \end{claim}
  Given this, we claim that $\beta_{b'} := \inf \{\beta_b : b \in B\}$ is achieved at some $b' \in B$ because it is a closed set.
  So for all $p \in \gamma_{r^*}$, we have $\inf_{u: d(U(p),u) \geq \epsilon} L(u;p) - L(u^*;p) \geq \alpha \beta_{b'}$.
\end{proof}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Bo: notes from chats with Raf about the separated result.

%%%%%%%%% third chat, May 20

%Main Thm: Show: for all r, r': for all p such that r' in gamma(p), we have
%inf_{u : psi(u) = r} L(u;p) - L(u*;p) >= delta * [ ell(r;p) - ell(r';p) ]
%
%Proof: fix p_canon in interior of gamma_{r'}
%Fix p_bd on boundary
%Show exists v such that inf_{u: psi(u) = r} L(u;p) - L(u*;p) >= v*p for all p between p_canon and p_bd
%Implies there exists delta > 0 such that inf_{u: psi(u) = r} L(u;p) - L(u*;p) >= delta * [ell(r;p) - ell(r';p)]
%Argue that p_bd comes from a closed set, so the inf over these delta is achieved at some delta > 0.
%
%
%Weaker lemma: Given r, r', p_canon, p_bd: show exists v such that
%inf_{u: psi(u) = r} L(u;p) - L(u*;p) >= v*p
%p*v > 0 for p in gamma_{r'} \ gamma_r
%p*v = 0 for p in gamma_{r'} \cap gamma_r .
%(for all p between p_canon and p_bd)
%Improved weaker lemma: case on p_bd in gamma_r or not.
%
%%%%%%%%% second chat

%let r1, r2, p be given with r1 in gamma(p).
%
%
%want inf_{u: psi(u) = r2} L(u;p) - L(u*;p) >= delta
%     -------------------------------------
%           ell(r2;p) - ell(r1;p)
%
%for each p, we get a delta > 0.
%
%
%
%
%Fix p. We have an optimal set U and "facets" (cell of the power diagram) {F}.
%
%Let d_f^y = nabla L_y(u_f).
%
%So given p, we have < p, d_f^y > is expected loss (plus something?)??
%
%Expected loss: sum_y p(y) L_y(u_f)
%            >=   sum_y p(y) (c_y + ||d_f^y|| epsilon)
%             =   c_y + epsilon <p, ||d_f||>
%
%L(u_f;p) - L(u_p;p)
%
% sum_y p(y) [ L_y(u_b) + d_f^y * (u_f - u_b) ] - sum_y p(y) L_y(u_b)
%
% = sum_y p(y) [ d_f^y * (u_f - u_b) ]
%>= sum_y p(y) [ delta_y * epsilon ]
%
%
%
%directions of steepest increase (slope)
%
%d_f exposes a face of U ... perhaps the face adjacent to the "facet" f?
%
%U = tall thin triangle example, even with arbitrarily steep slopes, can have arbitrarily low function values, even epsilon away from U!!!

%%%%%%%%%% first chat
%
%for all p, u:
%
%min_{embedded points} < p , L(u) - L(point) >
%
%>= delta * min_{r in R} < p , l(psi(u)) - l(r) >
%
%
%for all p, r' in gamma(p), r' \neq r:
%
%inf_{u : psi(u) = r} <p, L(u) - L(u_{r'})>  >=  delta <p, l(r) - l(r')>
%
%
%L_y(u) - L_y(u_{r'})        L_y(u_r) - L_y(u_{r'})
%
%
%
%Notice that whatever p is, its dot product with l(r) - l(r') is positive.
%So have to show that if p is close to dot-product zero on the left, it's also on the right.
%
%
%
%Draw the line from u_{r'} to u, eventually the slope becomes positive and stays positive for at least epsilon
%
%say d_y = "slope" toward u_{r'}
%
%
%let v = (u-u_{r'}) / ||u-u_{r'}||
%
%d_y = directional derivative in direction v (once positive)
%
%so I have <p, d_y*epsilon >

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%
%\break
%
%OLD, OUTDATED - Bo, May 5 2019
%
%\begin{lemma} \label{lemma:U-separated}
%  Let $\{U_j : j \in \mathcal{J}\} \subseteq \mathcal{U}$ be a subset of $\mathcal{U}$ with nonempty intersection, and let $U$ be some other member of $\mathcal{U}$.
%  Then one and only one of the following is true:
%  \begin{enumerate}
%    \item The intersection of the family and $U$ is nonempty, i.e. they all overlap at some point.
%    \item There exists $\epsilon > 0$ such that $d(U, \cap_{j \in \mathcal{J}} U_j) \geq \epsilon$.
%  \end{enumerate}

>>>>

\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage{mathtools, amsthm, amsmath, amssymb, graphicx, verbatim}
\usepackage{bbm}

\newcommand{\Comments}{1}
\newcommand{\mynote}[2]{\ifnum\Comments=1\textcolor{#1}{#2}\fi}
\newcommand{\mytodo}[2]{\ifnum\Comments=1%
  \todo[linecolor=#1!80!black,backgroundcolor=#1,bordercolor=#1!80!black]{#2}\fi}
\newcommand{\raf}[1]{\mynote{green}{[RF: #1]}}
\newcommand{\raft}[1]{\mytodo{green!20!white}{RF: #1}}
\newcommand{\jessie}[1]{\mynote{purple}{[JF: #1]}}
\newcommand{\jessiet}[1]{\mytodo{purple!20!white}{JF: #1}}
\newcommand{\bo}[1]{\mynote{blue}{[Bo: #1]}}
\newcommand{\botodo}[1]{\mytodo{blue!20!white}{[Bo: #1]}}
\ifnum\Comments=1               % fix margins for todonotes
  \setlength{\marginparwidth}{1in}
\fi

\newcommand{\reals}{\mathbb{R}}
\newcommand{\posreals}{\reals_{>0}}%{\reals_{++}}
\newcommand{\nonnegreals}{\reals_{\geq 0}}%{\reals_{++}}
\newcommand{\dom}{\mathrm{dom}}

@@

Given a convex set $Q \subseteq \reals^n$ and a point $p \in Q$, the \emph{cone of feasible directions} of $Q$ at $p$ is $F_Q(p) = \{v \in \reals^n: \exists \epsilon > 0 \text{ s.t. } p + \epsilon v \in Q\}$. The \emph{feasible subspace dimension} of $Q$ at $p$ is the dimension of the subspace $F_Q(p) \cap -F_Q(p)$.

Write it $FSD(Q,p)$.

\vskip1em
%Given a discrete loss $\ell: \R \times \Y \to \nonnegreals$, we say a loss $L: \reals^d \times \Y \to \nonnegreals$ \emph{indirectly elicits $\ell$} if there exists a ``link'' $\psi: \reals^d \to \R$ such that $\psi\left(\argmin_u L(u;p)\right) \subseteq \argmin_r \ell(r;p)$, for all $p$.
Given a finite property $\gamma: \Delta_{\Y} \to 2^{\R}$, we say a loss $L: \reals^d \times \Y \to \nonnegreals$ \emph{indirectly elicits $\gamma$} if there exists a ``link'' $\psi: \reals^d \to \R$ such that $\psi\left(\argmin_u L(u;p)\right) \subseteq \gamma(p)$, for all $p$.

\vskip1em
\begin{theorem}
  Suppose $L: \reals^d \times \Y \to \nonnegreals$ is convex for each $y$ and indirectly elicits $\gamma$. Then for all $p \in \Delta_{\Y}$ and all $r \in \gamma(p)$,
    \[ d \geq \|p\|_0 - FSD(\gamma_r, p) - 1 . \]
\end{theorem}
\begin{proof}[IN PROGRESS]
  Let $u \in \argmin_{u'} L(u';p)$ and let $r = \psi(u)$.
  This implies $p \in \gamma_r$.

  Because $L$ is convex, we have $\vec{0} \in \partial L(u;p)$.
  In particular, there exist $\{w_y \in \partial L(u,y) : y \in \Y\}$ such that $\sum_y p(y) w_y = \vec{0}$.

  Now consider any $p'$ such that $\sum_y p'(y) w_y = \vec{0}$.
  This implies that $u$ is also an optimal report for $p'$, so $p' \in \gamma_r$ as well.
  Hence, if we write $W \in \reals^{d \times y$ as a matrix whose columns are $w_y$, we have
    \[ \gamma_r \supseteq \{p' \in \Delta_{\Y} : p' W = \vec{0} \}.  \]
  or maybe?
    \[ \gamma_r \supseteq \{p' \in \Delta_{\Y} : (p'-p) W = \vec{0} \}.  \]
  This is an equation in $|\Y|-1$ nonnegative variables with $d$ constraints, so the dimensionality of its solution is \bo{CHECK} at least $|\Y|-d-1$.

  Note: If $\|p\|_0 < \|\Y|$, then everything drops down to that many dimensions because the zero coefficients from $p$ can be dropped from columns of the matrix, etc.

  To look into: do the ``flats'' always extend all the way to the edge of the simplex??

\end{proof}
